Synpotic Soil Characterization

### 2022-12-23 3-reports/characterization_report.Rmd
clean up markdown, simpler functions for all graphs

**Gravimetric moisture**

```{r moisture}
tar_read(gg_moisture)
```

**Loss on ignition (% organic matter)**

```{r loi}
tar_read(gg_loi)
```

**pH**

```{r pH}
tar_read(gg_pH)
```

**specific conductance**

```{r sp_cond}
tar_read(gg_sp_cond)
```

**total CNS**
```{r tctnts}
tar_read(gg_tctnts)
```

**Water extractable organic C**

```{r weoc}
tar_read(gg_weoc)
```

**Extractable inorganic N**

Inorganic N was extracted using 2M KCl

```{r din}
tar_read(gg_din)
```

**ICP results: base cations**

Extracted using 1M NH4Cl

```{r icp-base cations, fig.height=12, fig.width=7}
tar_read(gg_icp)$gg_base_cations
```

**ICP results: other cations**

Extracted using 1M NH4Cl

```{r icp-other cations, fig.height=9, fig.width=7}
tar_read(gg_icp)$gg_other_cations
```

**ICP results: others**

Extracted using 1M NH4Cl

```{r icp-others, fig.height=4, fig.width=7}
tar_read(gg_icp)$gg_others
```

@@

>>>>

## OVERALL SUMMARIES

### Analysis completion matrix

<details>
  <summary>click to open</summary>

Number of reps available per analysis. Most were 8-9 reps, but some (e.g. WLE B-horizons) had fewer reps.

```{r analyte-completion}
tar_read(analysis_completion_matrix) %>% knitr::kable()
```

### Overall trends - PCAs and Correlations

<details>
  <summary>click to open</summary>

**PCAs**

```{r overall-pca, fig.height=6, fig.width=6}
tar_read(gg_pca_all)$gg_pca_overall
```

```{r overall-pca-regions, fig.height=6, fig.width=12}
tar_read(gg_pca_all)$gg_pca_regions
```

**CORRELATIONS**

```{r correlations-all, fig.height=7, fig.width=7}
tar_read(gg_correlations)$corr_all
```

```{r correlations-regions, fig.height=8, fig.width=18}
tar_read(gg_correlations)$corr_regions
```

@@

## EACH ANALYSIS

### by transect

<details>
  <summary>click to open</summary>

```{r by_transect, fig.height=4, fig.width=10}
tar_read(gg_by_transect)
```

### by site - OA horizons

<details>
  <summary>click to open</summary>

```{r by_site_oa, fig.height=4, fig.width=10}
tar_read(gg_by_site_oa)
```

### by site - OAB horizons

<details>
  <summary>click to open</summary>

```{r by_site_oab, fig.height=4, fig.width=10}
tar_read(gg_by_site_oab)
```

## FT-ICR-MS

<details>
  <summary>click to open</summary>

```{r, icr-vk-domains, fig.height=5, fig.width=5}
tar_read(gg_icr_vankrevelen)$vk_domains
```

```{r, icr-vk-regions, fig.height=7, fig.width=16}
tar_read(gg_icr_vankrevelen)$vk_wle
tar_read(gg_icr_vankrevelen)$vk_cb

```

```{r, icr-unique, fig.height=16, fig.width=16}
tar_read(gg_icr_unique)
```

```{r, icr-pca, fig.height=5, fig.width=5}
tar_read(gg_icr_pca)$biplot_all
```

```{r, icr-pca-regions, fig.height=5, fig.width=10}
tar_read(gg_icr_pca)$biplot_regions
```

## Session Info
